Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-13 talk/iwtc11/paper.tex
cleared out some less relevant and inconsistent parts of the copied example

Let us now consider a simple ``interpreter'' function \lstinline{f} that uses the
object model (see the bottom of Figure~\ref{fig:objmodel}).
The loop in \lstinline{f} iterates \lstinline{y} times, and computes something in the process.
Simply running this function is slow, because there are lots of virtual method
calls inside the loop, one for each \lstinline{is_positive} and even two for each
call to \lstinline{add}. These method calls need to check the type of the involved
objects repeatedly and redundantly. In addition, a lot of objects are created
when executing that loop, many of these objects are short-lived.
The actual computation that is performed by \lstinline{f} is simply a sequence of
float or integer additions.

@@

The trace shows the inefficiencies of \lstinline{f} clearly, if one looks at
the number of \lstinline{new}, \lstinline{set/get} and \lstinline{guard_class}
operations. The number of \lstinline{guard_class} operation is particularly
problematic, not only because of the time it takes to run them. All guards also
have additional information attached that makes it possible to return to the
interpreter, should the guard fail. This means that too many guard operations also
consume a lot of memory.

In the rest of the paper we will see how this trace can be optimized using
partial evaluation.

>>>>

Let us now consider a simple ``interpreter'' function \lstinline{f} that uses the
object model (see the bottom of Figure~\ref{fig:objmodel}).
Simply running this function is slow, because there are lots of virtual method
calls inside the loop, one for each \lstinline{is_positive} and even two for each
call to \lstinline{add}. These method calls need to check the type of the involved
objects every iteration. In addition, a lot of objects are created
when executing that loop, many of these objects are short-lived.
The actual computation that is performed by \lstinline{f} is simply a sequence of
float or integer additions.

@@
